Your Paper Title

### 2025-06-01 Master Thesis/thesis.tex
New

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\usepackage{xcolor}
\usepackage{float}
\usepackage{tikz}
\usepackage{bm}
\usepackage{esvect} % 在导言区加入

@@

    \textbf{Major:} \\
    Theoretical Physics \\[1cm]

@@

In principle, there is another diagram contributing to this amplitude
\begin{figure}[H]
    \centering
    \includegraphics{sqcd6.pdf}
    \caption{MHV $\times$ anti-MHV}
\end{figure}
but because of the 3 particle special kinematics, the 3-point anti-MHV part gives vanishing contributtion, this diagram actually equals to 0. This is why we called this method MHV expansion in the following.

@@

For the NMHV ampitudes $A[1,2,3_1^+,4_1^-,5_2^+,6_2^-]$, we can obtain the following equation
\begin{align}
    A[1,2,3_1^+,4_1^-,5_2^+,6_2^-] =& \frac{\avg{24}\asbra{4}{P_{234}}{X}}{\avg{24}\asbra{3}{P_{234}}{X}}\times\frac{1}{s_{234}}\times\frac{\avg{61}\asbra{6}{P_{156}}{X}}{\avg{51}\asbra{5}{P_{156}}{X}}\notag\\
    &+\frac{\avg{26}\asbra{6}{P_{256}}{X}}{\avg{25}\asbra{5}{P_{256}}{X}}\times\frac{1}{s_{256}}\times\frac{\avg{14}\asbra{4}{P_{134}}{X}}{\avg{13}\asbra{3}{P_{134}}{X}}\notag\\
    &+\frac{\avg{26}^2\avg{61}}{\mdavg{25}{56}\asbra{2}{P_{34}}{X}\asbra{1}{P_{34}}{X}}\times\frac{1}{s_{34}}\times\frac{\asbra{4}{P_{34}}{X}^3}{\avg{34}\asbra{3}{P_{34}}{X}}\notag\\
    &+\frac{\avg{24}^2\avg{41}}{\mdavg{23}{36}\asbra{2}{P_{56}}{X}\asbra{1}{P_{56}}{X}}\times\frac{1}{s_{56}}\times\frac{\asbra{6}{P_{56}}{X}^3}{\avg{56}\asbra{5}{P_{56}}{X}}.
\end{align}
where I do not cancel the dependence of spinor X explicitly, but it is not quite complicated to do.
\subsubsection{n-point case}
Here, we first propose a compact formula for the color-ordered amplitude
\begin{equation}
    A=\frac{\asqu{2a}\!\asqu{1a}}{\underbrace{\avg{2\star}\cdots \avg{\star 1}}_{SU(N_1)}\underbrace{\avg{2\ast }\cdots \avg{\ast 1}}_{SU(N_2)}}
\end{equation}
where a refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
refers to the ordering for the second gauge group. We suppose there are $n_1$ gauge boson 1, $n_2$ gauge boson 2, so the n-point means that $n=n_1+n_2+2$.
\par
The usual way to prove this kind of compact formula is induction. First we suppose that all of the amplitudes with external point lower than n satisfy the compact formula.

\subsection{Pure scalar case}
Before going to the computation of pure scalar amplitudes in the 2-site model, it is necessary to review a quite similar amplitude -- scalar QED.
There are two feynman diagrams corresponding to 4 scalar scattering process 
\begin{figure}[H]
    \centering
    \includegraphics{s4pt.pdf}
    \caption{4 scalar scattering}
\end{figure}
First we can use the feynman rule to compute them like
\begin{align}
    i\mathcal{A}&=(-ie)^2(-i)\times\frac{(p_1-p_2)(p_3-p_4)}{(p_1+p_2)^2}+(-ie)^2(-i)\frac{(p_1-p_4)(p_3-p_2)}{(p_1+p_4)^2}\notag\\
    &=ie^2\left(\frac{u-t}{s}+\frac{u-s}{t}\right)\notag\\
    &=-2ie^2-2ie^2\left(\frac{t}{s}+\frac{s}{t}\right)
\end{align}
where the Mandelstam variables are defined as 
\begin{equation}
    s=(p_1+p_2)^2,\quad t=(p_1+p_4)^2,\quad u=(p_1+p_3)^2.
\end{equation}
We can rewrite this formula in terms of spinor-helicity variables
\begin{equation}
    s=\cbrak{12}{21}=\cbrak{34}{43},\quad t=\cbrak{14}{41}=\cbrak{23}{32},\quad u=\cbrak{13}{31}=\cbrak{24}{42}.
\end{equation}
then the amplitudes can be rewritten like
\begin{equation}
    \mathcal{A}=-2e^2-2e^2\left(\frac{\mdavg{14}{23}}{\mdavg{12}{34}}+\frac{\mdavg{12}{34}}{\mdavg{14}{23}}\right)
\end{equation}
The second term can be written further as
\begin{align}
    \frac{\mdavg{14}{23}}{\mdavg{12}{34}}+\frac{\mdavg{12}{34}}{\mdavg{14}{23}}&=\frac{\avg{14}^2\avg{23}^2+\avg{12}^2\avg{34}^2}{\mdavg{14}{23}\!\mdavg{12}{34}}=\frac{(\mdavg{14}{23}+\mdavg{12}{34})^2-2\mdavg{14}{23}\!\mdavg{12}{34}}{\mdavg{14}{23}\!\mdavg{12}{34}}\notag\\
    &=-\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}-2
\end{align}
then the final form of amplitudes can be read as
\begin{equation}
    \mathcal{A}=\underbrace{2e^2}_{\text{boundary term}}+2e^2\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
    \label{4.68}
\end{equation}
where the meaning of boundary term can be understood later.

@@

Similarly, if we consider four sclar scattering in 2-site model $\Phi\Phi^\dagger\Phi\Phi^\dagger$, we have the same Feynman diagram but with two different gauge boson propagating in the internal line
\begin{figure}[H]
    \centering
    \includegraphics{4ptt1.pdf}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics{4ptt2.pdf}
\end{figure}
These diagrams correspond to two different amplitudes
\begin{align}
    \mathcal{A}_1&=g_1^2\left(\frac{-2t-s}{s}\right)r_s+g_1^2\left(\frac{-2s-t}{t}\right)r_t\notag\\
    &=g_1^2\left(-1-2\frac{t}{s}\right)r_s+g_1^2\left(-1-2\frac{s}{t}\right)r_t\notag\\
    &=-g_1^2(r_s+r_t)-2g_1^2\left(\frac{t}{s}r_s+\frac{s}{t}r_t\right)
\end{align}
\subsection{Attempt to massive scalar}
It is quite intriguing to investigate what is the situation if we change the scalar to be massive. Without doubt, the BCFW shift should change and here we just refer to the method from \cite{Ballav:2020ese}.
The shift are choosen like 
\begin{gather}
    \aket{\hat{2^I}}=\aket{2^I},\qquad \sket{\hat{2^I}}=\sket{2^I}-\frac{z}{m}\sket{3}[2^I3]\\
    \aket{\hat{3}}=\aket{3}+\frac{z}{m}p_2\sket{3},\qquad \sket{\hat{3}}=\sket{3}.
\end{gather}
For the massive particle with same mass, it is necessary to introduce a x factor as \cite{Arkani-Hamed:2017jhn}. Here the x factor equals to
\begin{gather}
    x\lambda_{3\alpha}=\frac{p_{1\alpha\dot{\alpha}}}{m}\tilde{\lambda}_3^{\dot{\alpha}}\quad \Rightarrow \quad x\avg{\xi 3 }=\frac{\asbra{\xi}{p_1}{3}}{m}\qquad x=\frac{\asbra{\xi}{p_1}{3}}{m\avg{\xi 3}}\\
    \frac{\tilde{\lambda}_3^{\dot{\alpha}}}{x}=\frac{p_1^{\dot{\alpha \alpha}}\lambda_{3\alpha}}{m}\quad \Rightarrow \quad \frac{1}{x}[\xi3]=\frac{\asbra{3}{p_1}{\xi}}{m}\qquad \frac{1}{x}=\frac{\asbra{3}{p_1}{\xi}}{m[3\xi]} ~\text{or}~ x=\frac{m[\xi3]}{\asbra{3}{p_1}{\xi}}
\end{gather}
Then, from the 3-point building block
\begin{equation}
    M^{\text{min},+1}=x\frac{\avg{\textbf{12}}^{2s}}{m^{2s-1}},\qquad M^{\text{min,-1}}=\frac{1}{x}\frac{[\textbf{12}]^{2s}}{m^{2s-1}}
\end{equation}
here min means the minimal coupling. The amplitudes can be similarly computed by utlizing BCFW with some more efforts
\begin{align}
    A[\textbf{1},\textbf{2},3^+,4^+]&=g^2m \hat{x}_{12}\times\frac{1}{s_{12}}\times \frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=g^2m^2\frac{[4\hat{I}]}{\asbra{\hat{I}}{p_1}{4}}\times\frac{1}{s_{12}}\times \frac{[34]^3}{[4\hat{I}][\hat{I}\hat{3}]}
\end{align}
and
\begin{equation}
    -[3\hat{I}]\asbra{\hat{I}}{p_1}{4}
\end{equation}
can be computed as following
\begin{align}
    -[3\hat{I}]\asbra{\hat{I}}{p_1}{4}&=-[3|(p_3+p_4)p_1|4]=[3|p_3p_1|4]-[3|p_4p_1|4]=-[3|p_4p_1|4]\notag\\
    &=-p_{4\mu} p_{1\nu}[3|(\bar{\sigma}^\mu)^{\dot{\alpha}\beta}(\sigma^\nu)_{\beta\dot{\gamma}}|4]\notag\\
    &=[3|p_1p_4|4]-2p_1\cdot p_4[34]=-2p_1\cdot p_4[34]
\end{align}
here we use the formula
\begin{equation}
    (\sigma^\mu\bar{\sigma}^\nu+\sigma^\nu\bar{\sigma}^\mu)_\alpha^{\phantom{a}\beta}=2\eta^{\mu\nu}\delta_\alpha^{\phantom{a}\beta}
\end{equation}
and the term $2p_1\cdot p_4$ can be extracted from
\begin{equation}
    (p_1+p_4)^2=(p_2+p_3)^2=s_{23}
\end{equation}
The final result for this amplitude is 
\begin{equation}
    A[\textbf{1},\textbf{2},3^+,4^+]=\frac{[34]^3}{s_{34}(s_{23}-m^2)[43]}=m^2g^2\frac{[34]}{\avg{43}(s_{23}-m^2)}
\end{equation}
If we take the high energy limit so that the m can be chose to 0, then the amplitude becomes 0, which is consistent with our previous analysis.

>>>>

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black
}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\usepackage{xcolor}
\usepackage{float}
\usepackage{tikz}
\usepackage{bm}
\usepackage{esvect} % 在导言区加入

@@

    \textbf{Student number:} \\
    262309017 \\[1cm]

@@

In principle, there is another diagram contributing to this amplitude
\begin{figure}[H]
    \centering
    \includegraphics{sqcd6.pdf}
    \caption{MHV $\times$ anti-MHV}
\end{figure}
\noindent
but because of the 3 particle special kinematics, the 3-point anti-MHV part gives vanishing contributtion, this diagram actually equals to 0. This is why we called this method MHV expansion in the following.

@@

For the NMHV ampitudes $A[1,2,3_1^+,4_1^-,5_2^+,6_2^-]$, we can obtain the following equation
\begin{align}
    A[1,2,3_1^+,4_1^-,5_2^+,6_2^-] =& \frac{\avg{24}\asbra{4}{P_{234}}{X}}{\avg{24}\asbra{3}{P_{234}}{X}}\times\frac{1}{s_{234}}\times\frac{\avg{61}\asbra{6}{P_{156}}{X}}{\avg{51}\asbra{5}{P_{156}}{X}}\notag\\
    &+\frac{\avg{26}\asbra{6}{P_{256}}{X}}{\avg{25}\asbra{5}{P_{256}}{X}}\times\frac{1}{s_{256}}\times\frac{\avg{14}\asbra{4}{P_{134}}{X}}{\avg{13}\asbra{3}{P_{134}}{X}}\notag\\
    &+\frac{\avg{26}^2\avg{61}}{\mdavg{25}{56}\asbra{2}{P_{34}}{X}\asbra{1}{P_{34}}{X}}\times\frac{1}{s_{34}}\times\frac{\asbra{4}{P_{34}}{X}^3}{\avg{34}\asbra{3}{P_{34}}{X}}\notag\\
    &+\frac{\avg{24}^2\avg{41}}{\mdavg{23}{36}\asbra{2}{P_{56}}{X}\asbra{1}{P_{56}}{X}}\times\frac{1}{s_{56}}\times\frac{\asbra{6}{P_{56}}{X}^3}{\avg{56}\asbra{5}{P_{56}}{X}}.
\end{align}
where I do not cancel the dependence of spinor X explicitly, but it is not quite complicated to do.
\subsubsection{n-point case}
Here, we first propose a compact formula for the color-ordered amplitude
\begin{equation}
    A=\frac{\asqu{2a}\!\asqu{1a}}{\underbrace{\avg{2\star}\cdots \avg{\star 1}}_{SU(N_1)}\underbrace{\avg{2\ast }\cdots \avg{\ast 1}}_{SU(N_2)}}
\end{equation}
where $a$ refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
refers to the ordering for the second gauge group. We suppose there are $n_1$ gauge boson 1, $n_2$ gauge boson 2, so the n-point means that $n=n_1+n_2+2$.
\par
The usual way to prove this kind of compact formula is induction. First we suppose that all of the amplitudes with external point lower than n satisfy the compact formula.
Here, we denote the permutation $\star ~ \ast$ as $\sigma$ and $\tau$ respectively. It includes many kinds of channels as following
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{npt1.jpg}
    \caption{First type}
\end{figure}
The first channel can be computed like 
\begin{equation}
    A_1=\frac{\avg{\hat{2}a}^2\avg{1a}^2}{\avg{2\sigma(5)}\avg{\sigma(5)\sigma(6)}\cdots\avg{2\tau(n_1+1)}\cdots}\times\frac{1}{s_{\sigma(3)\sigma(4)}}\times\frac{[\hat{\sigma(3)}\sigma(4)]^3}{[\sigma(4)\hat{I}][\hat{I}\hat{\sigma(4)}]}
    \label{4.63}
\end{equation}
We also have other BCFW channels like
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{npt2.jpg}
    \caption{Second type}
\end{figure}
but this kind of channel always have a all-plus subamplitude, so it equals to 0.

And another channel can also be drawn like
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{npt3.jpg}
    \caption{Third type}
\end{figure}
\noindent
in which we still have an vanishing subamplitude in the right part.

The last one looks like 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{npt4.jpg}
    \caption{Fourth type}
\end{figure}
\noindent
and obviously, either the left or right part will offer a all-plus subamplitude, so that it equals to 0.

The equation \eqref{4.63} can be easily evaluated in the similar manner, and it actually gives us the form
\begin{equation}
    A=\frac{\asqu{2a}\!\asqu{1a}}{\avg{2\star}\cdots \avg{\star 1}\avg{2\ast }\cdots \avg{\ast 1}}
\end{equation}
so we accomplish the prove although it seems a little rough.
\subsection{Pure scalar case}
Before going to the computation of pure scalar amplitudes in the 2-site model, it is necessary to review a quite similar amplitude -- scalar QED.
There are two feynman diagrams corresponding to 4 scalar scattering process 
\begin{figure}[H]
    \centering
    \includegraphics{s4pt.pdf}
    \caption{4 scalar scattering}
\end{figure}
First we can use the feynman rule to compute them like
\begin{align}
    i\mathcal{A}&=(-ie)^2(-i)\times\frac{(p_1-p_2)(p_3-p_4)}{(p_1+p_2)^2}+(-ie)^2(-i)\frac{(p_1-p_4)(p_3-p_2)}{(p_1+p_4)^2}\notag\\
    &=ie^2\left(\frac{u-t}{s}+\frac{u-s}{t}\right)\notag\\
    &=-2ie^2-2ie^2\left(\frac{t}{s}+\frac{s}{t}\right)
\end{align}
where the Mandelstam variables are defined as 
\begin{equation}
    s=(p_1+p_2)^2,\quad t=(p_1+p_4)^2,\quad u=(p_1+p_3)^2.
\end{equation}
We can rewrite this formula in terms of spinor-helicity variables
\begin{equation}
    s=\cbrak{12}{21}=\cbrak{34}{43},\quad t=\cbrak{14}{41}=\cbrak{23}{32},\quad u=\cbrak{13}{31}=\cbrak{24}{42}.
\end{equation}
then the amplitudes can be rewritten like
\begin{equation}
    \mathcal{A}=-2e^2-2e^2\left(\frac{\mdavg{14}{23}}{\mdavg{12}{34}}+\frac{\mdavg{12}{34}}{\mdavg{14}{23}}\right)
\end{equation}
The second term can be written further as
\begin{align}
    \frac{\mdavg{14}{23}}{\mdavg{12}{34}}+\frac{\mdavg{12}{34}}{\mdavg{14}{23}}&=\frac{\avg{14}^2\avg{23}^2+\avg{12}^2\avg{34}^2}{\mdavg{14}{23}\!\mdavg{12}{34}}=\frac{(\mdavg{14}{23}+\mdavg{12}{34})^2-2\mdavg{14}{23}\!\mdavg{12}{34}}{\mdavg{14}{23}\!\mdavg{12}{34}}\notag\\
    &=-\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}-2
\end{align}
then the final form of amplitudes can be read as
\begin{equation}
    \mathcal{A}=\underbrace{2e^2}_{\text{boundary term}}+2e^2\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
    \label{4.68}
\end{equation}
where the meaning of boundary term can be understood later.

@@

Similarly, if we consider four sclar scattering in 2-site model $\Phi\Phi^\dagger\Phi\Phi^\dagger$, we have the same Feynman diagram but with two different gauge boson propagating in the internal line
\begin{figure}[H]
    \centering
    \includegraphics{4ptt1.pdf}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics{4ptt2.pdf}
\end{figure}
These diagrams correspond to two different amplitudes
\begin{align}
    \mathcal{A}_1&=g_1^2\left(\frac{-2t-s}{s}\right)r_s+g_1^2\left(\frac{-2s-t}{t}\right)r_t\notag\\
    &=g_1^2\left(-1-2\frac{t}{s}\right)r_s+g_1^2\left(-1-2\frac{s}{t}\right)r_t\notag\\
    &=-g_1^2(r_s+r_t)-2g_1^2\left(\frac{t}{s}r_s+\frac{s}{t}r_t\right)
\end{align}
It can also be found that the large-z behavior looks like
\begin{equation}
    \mathcal{A}_1|_{z\rightarrow\infty}=-g_1^2(r_s+r_t)
\end{equation}
if we choose $[1,3\rangle$ shift.

The color facor $r_s$ can be written like
\begin{equation}
    \mathrm{Tr}\{\Phi_1\Phi_2^\dagger T^a\}\mathrm{Tr}\{\Phi_3\Phi_4^\dagger T^a\}=\mathrm{Tr}\{\Phi_1\Phi_2^\dagger\Phi_3\Phi_4^\dagger\}-\frac{1}{N}\mathrm{Tr}\{\Phi_1\Phi_2^\dagger\}\mathrm{Tr}\{\Phi_3\Phi_4^\dagger\},
\end{equation}
where the subscript $i$ can be understood as the label of external particle. These two terms can remind that it is possible to introduce two independent operators into the Lagrangian:
\begin{equation}
    \mathcal{L}_{\text{4pt}}=\lambda_1\mathrm{Tr}\{\Phi\Phi^\dagger\Phi\Phi^\dagger\}+\lambda_2\mathrm{Tr}\{\Phi\Phi^\dagger\}\mathrm{Tr}\{\Phi\Phi^\dagger\}
\end{equation}
which can contribute to $r_s$ and $r_t$ at the same time. Therefore, if we choose the parameter
\begin{equation}
    \lambda_1=g_1^2,\qquad \lambda_2=\frac{g_2^2}{N}.
\end{equation}
The boundary term can be canceled so that we get a valid large-z behavior, then BCFW recursion relation can be utilized.

Unfortunately, if we consider the 3-site, in which there are two scalars, the pure scalar ampitudes will become quite complicated, so till now we postphone the discussion about that. 
\subsection{Attempt to massive scalar}
It is quite intriguing to investigate what is the situation if we change the scalar to be massive. Without doubt, the BCFW shift should change and here we just refer to the method from \cite{Ballav:2020ese}.
The shift are choosen like 
\begin{gather}
    \aket{\hat{2^I}}=\aket{2^I},\qquad \sket{\hat{2^I}}=\sket{2^I}-\frac{z}{m}\sket{3}[2^I3]\\
    \aket{\hat{3}}=\aket{3}+\frac{z}{m}p_2\sket{3},\qquad \sket{\hat{3}}=\sket{3}.
\end{gather}
For the massive particle with same mass, it is necessary to introduce a x factor as \cite{Arkani-Hamed:2017jhn}. Here the x factor equals to
\begin{gather}
    x\lambda_{3\alpha}=\frac{p_{1\alpha\dot{\alpha}}}{m}\tilde{\lambda}_3^{\dot{\alpha}}\quad \Rightarrow \quad x\avg{\xi 3 }=\frac{\asbra{\xi}{p_1}{3}}{m}\qquad x=\frac{\asbra{\xi}{p_1}{3}}{m\avg{\xi 3}}\\
    \frac{\tilde{\lambda}_3^{\dot{\alpha}}}{x}=\frac{p_1^{\dot{\alpha \alpha}}\lambda_{3\alpha}}{m}\quad \Rightarrow \quad \frac{1}{x}[\xi3]=\frac{\asbra{3}{p_1}{\xi}}{m}\qquad \frac{1}{x}=\frac{\asbra{3}{p_1}{\xi}}{m[3\xi]} ~\text{or}~ x=\frac{m[\xi3]}{\asbra{3}{p_1}{\xi}}
\end{gather}
Then, from the 3-point building block
\begin{equation}
    M^{\text{min},+1}=x\frac{\avg{\textbf{12}}^{2s}}{m^{2s-1}},\qquad M^{\text{min,-1}}=\frac{1}{x}\frac{[\textbf{12}]^{2s}}{m^{2s-1}}
\end{equation}
here min means the minimal coupling. The amplitudes can be similarly computed by utlizing BCFW with some more efforts
\begin{align}
    A[\textbf{1},\textbf{2},3^+,4^+]&=g^2m \hat{x}_{12}\times\frac{1}{s_{12}}\times \frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=g^2m^2\frac{[4\hat{I}]}{\asbra{\hat{I}}{p_1}{4}}\times\frac{1}{s_{12}}\times \frac{[34]^3}{[4\hat{I}][\hat{I}\hat{3}]}
\end{align}
and
\begin{equation}
    -[3\hat{I}]\asbra{\hat{I}}{p_1}{4}
\end{equation}
can be computed as following
\begin{align}
    -[3\hat{I}]\asbra{\hat{I}}{p_1}{4}&=-[3|(p_3+p_4)p_1|4]=[3|p_3p_1|4]-[3|p_4p_1|4]=-[3|p_4p_1|4]\notag\\
    &=-p_{4\mu} p_{1\nu}[3|(\bar{\sigma}^\mu)^{\dot{\alpha}\beta}(\sigma^\nu)_{\beta\dot{\gamma}}|4]\notag\\
    &=[3|p_1p_4|4]-2p_1\cdot p_4[34]=-2p_1\cdot p_4[34]
\end{align}
here we use the formula
\begin{equation}
    (\sigma^\mu\bar{\sigma}^\nu+\sigma^\nu\bar{\sigma}^\mu)_\alpha^{\phantom{a}\beta}=2\eta^{\mu\nu}\delta_\alpha^{\phantom{a}\beta}
\end{equation}
and the term $2p_1\cdot p_4$ can be extracted from
\begin{equation}
    (p_1+p_4)^2=(p_2+p_3)^2=s_{23}
\end{equation}
The final result for this amplitude is 
\begin{equation}
    A[\textbf{1},\textbf{2},3^+,4^+]=\frac{[34]^3}{s_{34}(s_{23}-m^2)[43]}=m^2g^2\frac{[34]}{\avg{43}(s_{23}-m^2)}
\end{equation}
If we take the high energy limit so that the m can be chose to 0, then the amplitude becomes 0, which is consistent with our previous analysis.
